Rates and delay times of type Ia supernovae in the Dark Energy Survey

### 2021-03-15 draft.tex
Updates from Overleaf

\label{sec:data}
\subsection{Dark Energy Survey supernova programme \label{subsec:des}}
To derive our sample of SNe and field galaxies, we make use of the Dark Energy Survey (DES). The DES Supernova Programme (DES-SN) was a transient survey based on five six-month seasons of observations of ten southern hemisphere fields with the Dark Energy Camera (DECam; \citealt{Flaugher2015}), designed primarily to measure the light curves of SNe Ia for use as cosmological distance indicators. Transients were detected and processed using a difference imaging program \citep{Kessler2015} and vetted using a machine learning (ML) algorithm \citep{Goldstein2015}. Spectral follow-up of live SN candidates was performed on a suite of large optical telescopes \citep{Smith2020a}, leading to the initial publication of a measurement of cosmological parameters using 207 spectroscopically confirmed SNe Ia (\citealt{DESCollaboration2018a}, and references therein). Spectroscopic redshifts for host galaxies come from the OzDES Global Redshift Catalog (GRC; \footnote{\url{https://docs.datacentral.org.au/ozdes/overview/dr2/}} \citealt{Yuan2015,Childress2017,Lidman2020}), which comprises galaxies targetted as DES-SN hosts with the OzDES programme as well as redshifts from legacy catalogues in the DES-SN fields.
\subsection{Supernovae \label{subsec:host_sample}}
\subsubsection{Photometric classification and quality cuts \label{subsubsec:sn_classify}}
With over 30,000 transients passing ML selection it was not possible to obtain spectral follow up of every object. Instead we make use of photometric classification in the form of the recurrent neural network classifier \texttt{superNNova} (SNN; \citealt{Moller2019}), foloowing the approach of \citet{Scolnic2020}. A full description of the training and fitting of SNN will be presented in Vincenzi et al. \textit{in prep} and M\"{o}ller et al. \textit{in prep}; we provide a brief overview here.

@@

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/mass_hist_linlog_sn_field_BC03.png}
    \caption{Upper: Distribution of the stellar mass of the SN host galaxies. The raw (green dashed) and spectroscopic-efficiency-weighted (blue dot-dashed; Section \ref{subsec:incompletenss_SN_hosts}) histograms are both normalised. Lower: As upper but for field galaxies, and shown on a log scale.  The distribution closely matches data from the ZFOURGE survey at $0.5<z<0.75$ (magenta dots). The difference between the raw counts (grey dotted) and the $V_{\mathrm{max}}$ corrected counts (orange solid; see Section \ref{sec:incompleteness}) is minimal. 
    \label{fig:mass_hist_hosts_field}}
\end{figure}

@@

The results of our SED fitting are shown in Fig. \ref{fig:mass_hist_hosts_field}. The figure showcases the vastly different distributions of the two samples. SN hosts are preferentially high mass galaxies, whereas the field galaxy distribution increases down to lower masses, peaking around $10^{8.5}~\mathrm{M}_{\odot}$. The SN host stellar mass distribution is plotted twice: once as raw counts; once weighted by the host galaxy spectroscopic efficiency (Section \ref{subsec:incompletenss_SN_hosts}). The field galaxy stellar mass distribution is shown on a log scale, along with the stellar mass function (SMF) from the ZFOURGE survey \citep{Tomczak2014} scaled to match at $\log (M/\mathrm{M}_{\odot}) = 10$, whose stellar masses are derived with the same photo-$z$ code, IMF and template library as used here. Above $10^{8.5}~\mathrm{M}_{\odot}$, the DES field galaxy distribution closely follows the ZFOURGE SMF for $0.5<z<0.75$, indicating that the DES sample is representative of field galaxies in this mass and redshift range.%To estimate uncertainties on the physical properties, we resample the photometry from a Gaussian distribution formed by the flux measurements and their uncertainties and rerun the SED fit. This procedure is repeated 1000 times. 
%%%% INCOMPLETENESS %%%%

>>>>

\label{sec:data}
\subsection{Dark Energy Survey supernova programme \label{subsec:des}}
To derive our sample of SNe and field galaxies, we make use of the Dark Energy Survey (DES). The DES Supernova Programme (DES-SN) was a transient survey based on five six-month seasons of observations of ten southern hemisphere fields with the Dark Energy Camera (DECam; \citealt{Flaugher2015}), designed primarily to measure the light curves of SNe Ia for use as cosmological distance indicators. Transients were detected and processed using a difference imaging program \citep{Kessler2015} and vetted using a machine learning (ML) algorithm \citep{Goldstein2015}. Spectral follow-up of live SN candidates was performed on a suite of large optical telescopes \citep{Smith2020a}, leading to the initial publication of a measurement of cosmological parameters using 207 spectroscopically confirmed SNe Ia (\citealt{DESCollaboration2018a}, and references therein). Spectroscopic redshifts for host galaxies come from the OzDES Global Redshift Catalog (GRC; \footnote{\url{https://docs.datacentral.org.au/ozdes/overview/dr2/}} \citealt{Yuan2015,Childress2017,Lidman2020}), which comprises galaxies targetted as DES-SN hosts with the OzDES programme as well as redshifts from legacy catalogues in the DES-SN fields.
\subsection{Supernovae \label{subsec:host_sample}}
\subsubsection{Photometric classification and quality cuts \label{subsubsec:sn_classify}}
With over 30,000 transients passing ML selection it was not possible to obtain spectral follow up of every object. Instead we make use of photometric classification in the form of the recurrent neural network classifier \texttt{superNNova} (SNN; \citealt{Moller2019}), following the approach of \citet{Scolnic2020}. A full description of the training and fitting of SNN will be presented in Vincenzi et al. \textit{in prep} and M\"{o}ller et al. \textit{in prep}; we provide a brief overview here.

@@

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/mass_hist_linlog_sn_field_BC03.png}
    \caption{Upper: Distribution of the stellar mass of the SN host galaxies. The raw (green dashed) and spectroscopic-efficiency-weighted (blue dot-dashed; Section \ref{subsec:incompletenss_SN_hosts}) histograms are both normalised. Comparison samples are PTF (purple; \citealt{Pan2014}) and Pantheon (orange; \citealt{Scolnic2018}). Lower: As upper but for field galaxies, and shown on a log scale.  The distribution closely matches data from the ZFOURGE survey at $0.5<z<0.75$ (magenta dots). The difference between the raw counts (grey dotted) and the $V_{\mathrm{max}}$ corrected counts (orange solid; see Section \ref{sec:incompleteness}) is minimal. 
    \label{fig:mass_hist_hosts_field}}
\end{figure}

@@

The results of our SED fitting are shown in Fig. \ref{fig:mass_hist_hosts_field}. The figure showcases the vastly different distributions of the two samples. SN hosts are preferentially high mass galaxies, whereas the field galaxy distribution increases down to lower masses, peaking around $10^{8.5}~\mathrm{M}_{\odot}$. The SN host stellar mass distribution is plotted twice: once as raw counts; once weighted by the host galaxy spectroscopic efficiency (Section \ref{subsec:incompletenss_SN_hosts}). As shown in Fig. \ref{fig:mass_hist_hosts_field}, the host stellar mass distribution of the DES-SN sample used in this analysis is qualitatively similar to that from the low redshift Palomar Transient Factory (PTF) sample \citep{Pan2014} as well as the large cosmological Pantheon sample \citep{Scolnic2018}. This consistency reflects that seen in the smaller spectroscopically confirmed samples presented in \citet{Wiseman2020} and \citet{Smith2020}. The field galaxy stellar mass distribution is shown on a log scale, along with the stellar mass function (SMF) from the ZFOURGE survey \citep{Tomczak2014} scaled to match at $\log (M/\mathrm{M}_{\odot}) = 10$, whose stellar masses are derived with the same photo-$z$ code, IMF and template library as used here. Above $10^{8.5}~\mathrm{M}_{\odot}$, the DES field galaxy distribution closely follows the ZFOURGE SMF for $0.5<z<0.75$, indicating that the DES sample is representative of field galaxies in this mass and redshift range.%To estimate uncertainties on the physical properties, we resample the photometry from a Gaussian distribution formed by the flux measurements and their uncertainties and rerun the SED fit. This procedure is repeated 1000 times. 
%%%% INCOMPLETENESS %%%%
